Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-10-25 analysis/paper/paper.Rmd
Use ";" not "," between refs to tables and figs

When predicting the availability of data availability as compared with *Phytopathology*®, publications in one journal, *Phytopathologia Mediterranea*, can be considered clearly more likely to share data than publications in *Phytopathology*®, but no effects were detectable in any other journal title (Figure \@ref(fig:journal-parameters)B, Table S2).

@@

There was no clear effect for year when predicting the availability of computational methods as the analysis results were undecided (Figure \@ref(fig:year-parameters)A, Table S3).

However, the year of publication did not have an effect on the availability of data was accepted (Figure \@ref(fig:year-parameters)B, Table S4).
The effect of year (Median = 0.08, 95% CI [-8.06e-03, 0.18]) had a 96.19% probability of being positive (> 0), 75.92% of being significant (> 0.05), and 0.00% of being large (> 0.30).
The estimation successfully converged (Rhat = 1.000) and the indices were reliable (ESS = 21692).

>>>>

When predicting the availability of data availability as compared with *Phytopathology*®, publications in one journal, *Phytopathologia Mediterranea*, can be considered clearly more likely to share data than publications in *Phytopathology*®, but no effects were detectable in any other journal title (Figure \@ref(fig:journal-parameters)B; Table S2).

@@

There was no clear effect for year when predicting the availability of computational methods as the analysis results were undecided (Figure \@ref(fig:year-parameters)A; Table S3).

However, the year of publication did not have an effect on the availability of data (Figure \@ref(fig:year-parameters)B, Table S4).

The effect of year (Median = 0.08, 95% CI [-8.06e-03, 0.18]) had a 96.19% probability of being positive (> 0), 75.92% of being significant (> 0.05), and 0.00% of being large (> 0.30).
The estimation successfully converged (Rhat = 1.000) and the indices were reliable (ESS = 21692).
